Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
Cut down orphan

Assessing whether DP improved task performance (h3) was difficult given the small sample size of our study and large number of factors influencing each person's performance.  While tasks were completed on average slightly faster than the control interface, these differences were not statistically significant.  However, more data sources seemed to be consulted (we use ``seemed'' carefully because these findings approached significance) during trials with DP over the control interface, which meant that people were looking at more diverse information than the control conditions.  We also found that participants justified their choices with a greater number of factors in DP than the control interface, suggesting that decisions may have been made considering a greater number of factors.  Participants entertained more possibilities for longer in the DP trial, while participants were more prone to eliminate candidates early in the baseline interface.  Finally, people took fewer notes in the DP condition than the baseline, suggesting that there was less need for external cognitive support in DP, which strongly indicates that DP made the task easier to complete.

>>>>

Assessing whether DP improved task performance (h3) was difficult given the small sample size of our study and large number of factors influencing each person's performance.  Tasks were completed on average slightly faster than the control interface, but not statistically significantly.  However, more data sources seemed to be consulted (we use ``seemed'' carefully because these findings approached significance) during trials with DP over the control interface, which meant that people were looking at more diverse information than the control conditions.  We also found that participants justified their choices with a greater number of factors in DP than the control interface, suggesting that decisions may have been made considering a greater number of factors.  Participants entertained more possibilities for longer in the DP trial, while participants were more prone to eliminate candidates early in the baseline interface.  Finally, people took fewer notes in the DP condition than the baseline, suggesting that there was less need for external cognitive support in DP, which strongly indicates that DP made the task easier to complete.\looseness=-1
